Lucy.js: Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex
Minor

Many applications on the web today use a combination of client-side and server-side data stores to facilitate fast interactive and data-intensive experiences. 
However, standard client side databases within browsers do not currently support full-text searching, and it is not clear the best way to engineer full-text indexes on top of the existing infrastructure.
In this paper, we introduce Lucy.js, a fully client-side search engine built as an extension of the existing well-supported IndexedDB API.
We compare the performance of the different indexes we implement on different types of full-text content and queries. We find that a hybrid approach combining inverted indexes and tries perform the best, particularly on larger datasets.
We also implement various real-life applications of our system and compare the performance of our system with that of using a fully server side system. We find that given the costs of network latency, our approach is significantly faster than relying on a server-side search engine.
Finally, we discuss how our system may open up novel web application and data storage designs that solely use client-side search engines or combine both client and server search engines.
\end{abstract}

>>>>

Many applications on the web today use a combination of client-side and server-side data stores to facilitate fast interactive and data-intensive experiences. 
However, standard client side databases within browsers do not currently support full-text searching, and it is not clear the best way to engineer full-text indexes on top of the existing infrastructure.
In this paper, we introduce Lucy.js, a fully client-side search engine built as an extension of the existing well-supported IndexedDB API.
We compare the performance of the different indexes we implement, on different types of full-text content and queries. We find that a hybrid approach combining inverted indexes and tries performs the best, particularly on larger datasets.
We also implement various real-life applications of our system and compare the performance of our system with that of using a fully server side system. We find that given the costs of network latency, our approach is significantly faster than relying on a server-side search engine.
Finally, we discuss how our system may open up novel web application and data storage designs that solely use client-side search engines or combine both client and server search engines.
\end{abstract}
